---
title: "Assessment 1.1"
author: "Sandy Fairbairn Student ID s3874811"
date: "19/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RMarkdown **editing** _editing_ 

[Rstudio](www.rstudio.com)


fastfood <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')


knitr::kable(head(fastfood[1:10,]), "pipe")

knitr::kable(fastfood[1:10, 1:5], "pipe")

```R
fastfood <-fastfood %>%
filter(total_fat>40 & total_cab>80)

```
### Part 2

```R
skimr(fastfood)
```

fastfood <- fastfood(restaurant = c(),

```{r}
fastfood %>% group_by(restuarant) %>% summarise(avr_calories=mean(calories),
```

fastfood <- c("total calories"),
total_calories <- c(1800)
df <- data.frame(total_calories)

```{r}
fastfood %>% 
      ggplot(aes(x=total_fat, y=total_carb))+
      geom_point()+
            geom_smooth(method = "lm")
   

##Part 3

survey <- survey %>%
  mutate(timestamp = mdy_hms(timestamp),
         age_category = fct_relevel(fct_reorder(how_old_are_you, parse_number(how_old_are_you)), "under 18"),
         experience_overall = str_replace(overall_years_of_professional_experience, " - ", "-"),
         experience_overall = fct_reorder(experience_overall, parse_number(experience_overall)),
         experience_in_field = str_replace(years_of_experience_in_field, " - ", "-"),
         experience_in_field = fct_reorder(experience_in_field, parse_number(experience_in_field))) %>%
  mutate(gender = fct_collapse(coalesce(gender, "Other or prefer not to answer"), "Other or prefer not to answer" = c("Other or prefer not to answer", "Prefer not to answer")),
         race = fct_lump(coalesce(race, "Other"), 4),
         age=parse_number(how_old_are_you))

survey_usd <- survey %>%
  filter(currency == "USD") %>%
  filter(annual_salary >= 5000,
         annual_salary <= 2e6) %>%
  mutate(state = str_remove(state, ", .*"))

calories_type %>%
  ggplot(aes(age,annual_salary)) +
  geom_col()+
  coord_flip()





