---
## Sandy Fairbairn
**s3874811**

---

# Assignment 2

---

output: html_document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

```


```{r}
data<-read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv')
```

#Part 1 formatting RMarkdown document


#1. Create an Rmarkdown document with webpage as output (same as in setup)

---
## Sandy Fairbairn 
## **s3874811**
---
# Assignment 2
---



#Part 2 Data Wrangling and visualization

# 1. Display the first 10 rows of the dataset using `kable()` function

```{r}
knitr::kable(data[1:10,1:5])
```

#2. Using `skim()` display the summary of variables. 

Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type?  Write 2-3 sentences with your explanation.

These variables, together with job retails, neighbourhood type, and age, might be helpful in predicting family income. When considering the inclusion of other factors such as gender and US region, the data might become more complex and confusing to those who would be reviewing the data set.
```{r}
library(skimr)
skim(data)
```


#3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`

```{r}
library(tidyverse)
data<- data %>% mutate(family_income = fct_reorder(family_income, parse_number(family_income)))
```


#4. What is the number of people who celebrate? 

Number of people celebrate? 980
```{r}
data %>% count(celebrate)
```


#5. What are categories and insights for each main dish served and the method it is prepared?
```{r}
data %>% count(main_dish, main_prep)
data %>% count(main_prep)
```

#6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes. 

Write 2-3 sentences with your explanation of each insight.

The graphs for both the turkey and the chicken indicate that both baked and roasted were on the same level. While ham/pork had a high % for only baked and roasted, it had an extremely lengthy percentage value for both baked and roasted. Take a look at this: the most popular main meal served over the Thanksgiving holiday was ham or pork.

```{r}        
data$main_dish<-as.factor(data$main_dish)
data$main_prep<-as.factor(data$main_prep)
data$gender<-as.factor(data$gender)

data%>% filter(main_dish == "Turkey") %>%
  ggplot(aes(main_dish, fill=(main_prep)))+ geom_bar()

data%>% filter(main_dish == "Chicken") %>%
  ggplot(aes(main_dish, fill=(main_prep)))+ geom_bar()

data%>% filter(main_dish == "Ham/Pork") %>%
  ggplot(aes(main_dish, fill=(main_prep)))+ geom_bar()


```

#7. How many use cranberry sauce? 
How many use cranberry sauce? 803
How many use gravy? 892
```{r}
data %>% count(gravy == "Yes") 
data %>% count(cranberry == "Canned" | cranberry == "Homemade" | cranberry == "other please speify)")
```
#8. What is the distribution of those who celebrate across income ranges.

Create a data viz.Write 2-3 sentences with your explanation of each insight.

According to the ggplot graph, the Yes (celebrate) response percentage was higher among families with a common family income in the $25-$49K range. Then the Yes (Celebrate) responses for the 50K to 99K were equal, with a larger No (Celebrate) response for the 50K to 75K. In contrast, the Yes (Celebrate) earned $200K in income, which outperformed the income value between 125K and 199K for the No (Celebrate) (celebrate).


```{r}
data_new1$celebrate<-as.factor(data_new1$celebrate)

data_new1 %>% filter(family_income != "Prefer not to answer") %>%
  ggplot(aes(family_income, fill = celebrate))+
  geom_bar(position = "dodge", alpha = .8)+
  theme_minimal()+
  coord_flip()+
  labs(y= "number of people")


```
  

`
#10. Use the following code to create a new data set 2 mark

Write 2-3 sentences with your explanation of what it does

Utilizing three variables from an existing dataset as the foundation for the coding, it then creates a new dataset using the data from the three variables. This is followed by an examination of particular phrasing, which is subsequently eliminated from the new data collection With the new data set, it also looks for a unique id, which is then used to extract the data from the subset variables, as previously stated.


```{r}
library(dplyr)
data_new2<- data %>% select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
```


#11. Intall package `widyr` and use `pairwise_cor()` function 

Write 2-3 sentences with your explanation of what it does

It establishes a pairwise correlation between two or more columns and then assesses the output of the correlation between these two columns, as seen in the following example. It does this by searching for certain keywords in the first column and matching those terms to the words in the second column, as seen below.

```{r}
library(widyr)
data_new2%>% pairwise_cor(value, id, sort = TRUE)
```


#13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset

 Compare 3 models using different set of input variables. Use different number of variables.

#Explain your choice of variables (3 sentences) 

I have utilized the gender variables as the primary variables, and then broken these down using the variables for the main dish. All three provide estimates with an error rate of more than 45 percent.

#Write 2 sentences explaining which model os best.

The randomforest model was the easiest for me to grasp the coding processes. Given that I am not a programmer, randomForest in R studio was the most straightforward and simple to follow when looking at the new data variables.

```{r}
library(randomForest)

random_fr_Mod1<-randomForest(gender~celebrate+main_dish+stuffing, data=data_new1, na.action=na.omit)

random_fr_Mod2<-randomForest(gender~celebrate+main_dish+main_prep, data=data_new1, na.action=na.omit)

random_fr_Mod3<-randomForest(gender~celebrate+main_dish+age, data=data_new1, na.action=na.omit)

print(random_fr_Mod1)
print(random_fr_Mod2)
print(random_fr_Mod3)
```

#### Resources:

RMarkdown tutorial https://rmarkdown.rstudio.com/lesson-1.html

ggplot2: Elegant Graphics for Data Analysis https://ggplot2-book.org/